---
title: "Apikolada - Request data from kolada.se"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{kolada_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Setup
```{r setup}
library(apikolada)
```

# Usage

This package provides infrastructure to request data from the kolada.se API in order to get informatioin about different KPIs from different periods and cities in Sweden. 

* get_all_kpis(): function that returns an overview of all the possible KPIs that can be requested
* get_all_cities(): function that returns an overview of all the possible cities that can be requested
* get_infos(): function that is used to request the data from the API, all three parameters kpis, cities and years are vectors that have to be specified

# Example query

In the following, an example query is shown, which requests the following information:

* **KPIs**: 
    1. N02904 - *Invånare 0-19 år i ekonomiskt utsatta hushåll, andel (%) *
    2. U28116 - *Enheterna har individuellt utformade mål i genomförandeplanen för de boende* 
* **Cities**: Helsingborg, Askersund
* **Years**: 2017, 2018, 2019
  
```{r}
# import the package
library(apikolada)

get_infos(kpis = c("N02904", "U28116"), 
          cities = c("Göteborg", "Malmö"), 
          years = c(2017,2018,2019))


```
